This is the title [Article v\versionnumber]

### 2022-05-19 manuscript/manuscript.tex
Bugfixes in the tutorial part

@@

For easier post-processing, we will use grids that contain the whole molecule.
This could in theory be avoided for streptavidin and the complex, since only the surrounding of the biotin molecule (i.e., the binding pocket) is required for the analysis.
We also recommend that you center the molecule in space.
For each system (biotin, streptavidin, complex), produce a centered pdb file using \software{cpptraj}:
\begin{lstlisting}
parm solvated.parm7
trajin md-01.nc 1 1 1
autoimage !(:WAT) origin
strip :WAT
trajout solute-centered.pdb
\end{lstlisting}
Then, find the extent (minimum and maximum) of the x-, y-, and z-coordinates for each system.
This can be done e.g., using the \software{mdtraj} package in Python.
\begin{lstlisting}[style=python]
import mdtraj as md
pdb = md.load("solute-centered.pdb")
# mdtraj converts to nm.
# *10 to convert back to Angstrom.
min = pdb.xyz[0].min(0) * 10.
max = pdb.xyz[0].max(0) * 10.
print(*list(zip("xyz", min, max)), sep="\n")
\end{lstlisting}
Then, decide on grid dimensions for every system.
For a system centered at the origin with a spacing of \SI{0.5}{\angstrom} and a buffer of, e.g., \SI{7}{\angstrom} between the solute and the grid wall, you need $4.0\times (d+7)$ bins in the respective direction, where $d$ is the larger of $-$min and $+$max in the respective direction.
We note that this centered grid is usually larger than it needs to be in some directions.
If you want to save some extra memory and calculation time, feel free to align the grid more precisely to the minimum and maximum coordinates, or use a smaller grid that only covers the binding pocket.
You can also rotate the molecule by its principal axes to fit the cuboid grid more exactly.
However, this needs to be done \emph{before} the MD run, since rotating the trajectory damages the periodic box information.

@@

Alternatively, one can note that the solvent-solvent energy in a sufficiently large GIST grid converges to the correct bulk value at large distance to the solute.
This means that the reference energy can be obtained from a large GIST grid by binning the voxels by their distance to the solute, and evaluate Equation \ref{eq_ewwref} within each bin.
If this value converges to a constant, this can be used as $E_{ww}^\textit{ref}$.

@@

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
gist = gt.gist.load_gist_file(
    "gist.dat", struct="solute-centered.pdb")
bins, eww = gist.rdf(
    "Eww_unref", bins=100, rmax=20., normalize="norm")
plt.plot(bins, eww)
eww_auto = gist.detect_reference_value().values[0]
plt.axhline(eww_auto, color='k')
plt.gca().set(
    xlabel='distance [A]', ylabel='E_ww per mol')
plt.show()
\end{lstlisting}

@@

Now, add all free energy contributions to obtain the spatially resolved $\dgsolv$.
In \software{gisttools}, this is done automatically (simply use the \inlinecode{A\_dens} and \inlinecode{A\_norm} columns).
In \software{gistpp}, use the \inlinecode{add} command, with the same syntax as the \inlinecode{div} command used above.
After that, check whether your free energy contributions become negligible at high distances to the solute.
In a plot like Figure~\ref{fig_ewwref} based on the \inlinecode{A\_dens} column, the values should tend to zero.
However, it is more informative to plot the cumulative free energy contribution against the distance to the solute, to check the convergence.
It the curve flattens out, this is your final $\dgsolv$.
If it does not, you might need to tweak the Eww reference, or introduce a reference value for the entropy (especially with older versions of \software{cpptraj}).

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
# adapt eww_ref!
gist = gt.gist.load_gist_file("gist.dat",
    struct="solute-centered.pdb", eww_ref=-9.533)
bins, (dg, eww, esw, s) = gist.rdf(
    ["A_dens", "Esw_dens", "Eww_dens", "dTSsix_dens"],
    bins=100, rmax=20., normalize="none")
plt.plot(bins, np.cumsum(dg), label="dG")
plt.plot(bins, np.cumsum(eww), label="Eww")
plt.plot(bins, np.cumsum(esw), label="Esw")
plt.plot(bins, np.cumsum(s), label="dS")
\end{lstlisting}

@@

\begin{lstlisting}
load solute-centered.pdb
show sticks, resname BTN
as surface, not resname BTN
load gist-gO.dx, gO
isosurface gO_high, gO, 2.
\end{lstlisting}

>>>>

% NOTES
% when importing references from EndNote, remove the type = {Journal Article}. It messes with the livecoms bibtex style somehow...
% Place a \@ between all-caps words and punctuation ("This is a sentence about GIST\@. This is ...")
% Place a protected space (~) between "Figure" and the reference. The same with tables.

@@

For easier post-processing, we will use grids that contain the whole molecule.
This could in theory be avoided for streptavidin and the complex, since only the surrounding of the biotin molecule (i.e., the binding pocket) is required for the analysis.
We also recommend that you center the molecule in space.
For each system (biotin, streptavidin, complex), produce a centered pdb file using \software{cpptraj}:
\begin{lstlisting}
parm solvated.parm7
trajin md-01.nc 1 1 1
autoimage !(:WAT) origin
strip :WAT
trajout solute-centered.pdb
\end{lstlisting}
Then, find the extent (minimum and maximum) of the x-, y-, and z-coordinates for each system.
This can be done e.g., using the \software{mdtraj} package in Python.
\begin{lstlisting}[style=python]
import mdtraj as md
pdb = md.load("solute-centered.pdb")
# mdtraj converts to nm.
# *10 to convert back to Angstrom.
min = pdb.xyz[0].min(0) * 10.
max = pdb.xyz[0].max(0) * 10.
print(*list(zip("xyz", min, max)), sep="\n")
\end{lstlisting}
Then, decide on grid dimensions for every system.
For a system centered at the origin with a spacing of \SI{0.5}{\angstrom} and a buffer of, e.g., \SI{7}{\angstrom} between the solute and the grid wall, you need $4.0\times (d+7)$ bins in the respective direction, where $d$ is the larger of $-$min and $+$max in the respective direction.
\todo{this does not work with the default gisttools values for the automatic detection of the energy reference. Better use a larger value. }
We note that this centered grid is usually larger than it needs to be in some directions.
If you want to save some extra memory and calculation time, feel free to align the grid more precisely to the minimum and maximum coordinates, or use a smaller grid that only covers the binding pocket.
You can also rotate the molecule by its principal axes to fit the cuboid grid more exactly.
However, this needs to be done \emph{before} the MD run, since rotating the trajectory damages the periodic box information.

@@

Alternatively, one can note that the solvent-solvent energy in a sufficiently large GIST grid converges to the correct bulk value at large distance to the solute.
This means that the reference energy can be obtained from a large GIST grid by binning the voxels by their distance to the solute, and evaluate Equation~\ref{eq_ewwref} within each bin.
If this value converges to a constant, this can be used as $E_{ww}^\textit{ref}$.

@@

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
gist = gt.gist.load_gist_file(
    "gist.dat", struct="solute-centered.pdb")
bins, eww = gist.rdf(
    "Eww_unref_norm", bins=100, rmax=20., normalize="norm")
plt.plot(bins, eww)
eww_auto = gist.detect_reference_value().values[0]
plt.axhline(eww_auto, color='k')
plt.gca().set(
    xlabel='distance [A]', ylabel='E_ww per mol')
plt.show()
\end{lstlisting}

@@

Now, add all free energy contributions to obtain the spatially resolved $\dgsolv$.
In \software{gisttools}, this is done automatically (simply use the \inlinecode{A\_dens} and \inlinecode{A\_norm} columns).
In \software{gistpp}, use the \inlinecode{add} command, with the same syntax as the \inlinecode{div} command used above.
After that, check whether your free energy contributions become negligible at high distances to the solute.
In a plot like Figure~\ref{fig_ewwref} based on the \inlinecode{A\_dens} column, the values should tend to zero.
However, it is more informative to plot the cumulative free energy contribution against the distance to the solute, to check the convergence.
It the curve flattens out, this is your final $\dgsolv$\@.
If it does not, you might need to tweak the Eww reference, or introduce a reference value for the entropy (especially with older versions of \software{cpptraj}).

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
# adapt eww_ref!
gist = gt.gist.load_gist_file("gist.dat",
    struct="solute-centered.pdb", eww_ref=-9.533)
bins, (dg, esw, eww, s) = gist.rdf(
    ["A_dens", "Esw_dens", "Eww_dens", "dTSsix_dens"],
    bins=100, rmax=20., normalize="none")
plt.plot(bins, np.cumsum(dg), label="dG")
plt.plot(bins, np.cumsum(eww), label="Eww")
plt.plot(bins, np.cumsum(esw), label="Esw")
plt.plot(bins, np.cumsum(s), label="dS")
\end{lstlisting}

@@

% The current font makes the O look like a tofu / placeholder
\begin{lstlisting}
load solute-centered.pdb
show sticks, resname BTN
as surface, not resname BTN
load gist-gO.dx, gO
isosurface gO_high, gO, 2.
\end{lstlisting}
